Figure 6 - networks

### 2024-08-05 ms_figure_6_networks.Rmd
Swap panel order FigS6

## Put together
figs6a <- cowplot::plot_grid(
    cowplot::plot_grid(
        tplot, 
        get_legend(ggeqn1, "right"), 
        similplot + theme(legend.position = "bottom"), 
        ggr150example + theme(legend.position = "none"), 
        align = "v", axis = "t", 
        labels = c("A", "", "", ""), nrow = 1, 
        rel_widths = c(1.1, 0.9, 1, 0.5)
    ),
    ggeqn2, ncol = 1, labels = "", 
    rel_heights = c(3, 1)
)
```

@@

plot_grid(
    figs6a, 
    plot_grid(hm_rad, ggtbl, nrow = 1, align = "h", axis = "b", 
              rel_widths = c(2, 2.5), labels = c("B", "C")),
    rel_heights = c(1, 3), ncol = 1,
    labels = c("A", "")
)
```

>>>>

## Put together
figs6c <- cowplot::plot_grid(
    cowplot::plot_grid(
        tplot, 
        get_legend(ggeqn1, "right"), 
        similplot + theme(legend.position = "bottom"), 
        ggr150example + theme(legend.position = "none"), 
        align = "v", axis = "t", 
        labels = c("C", "", "", ""), nrow = 1, 
        rel_widths = c(1.1, 0.9, 1, 0.5)
    ),
    ggeqn2, ncol = 1, labels = "", 
    rel_heights = c(3, 1)
)
```

@@

plot_grid(
    plot_grid(hm_rad, ggtbl, nrow = 1, align = "h", axis = "b", 
              rel_widths = c(2, 2.5), labels = c("A", "B")),
    figs6c, 
    rel_heights = c(3, 1), ncol = 1,
    labels = c("", "")
)
```
